The Linear Instability of Dilute Ultrarelativistic \epm\ Pair Beams

### 2016-08-08 oblique.tex
more updates

Because there is little variation in the maximal oblique growth rate as a wavevector orientation, we plot the maximum growth rate as a function of $T_b$
and $\gammabeam - 1$ in Figure \ref{fig:OGgen}.  Here for relativistic beams, the maximum growth rate varies
little with $T_b$, varying by less than $10\%$ between hot and cold beams and 
we find:
\begin{equation}
\Gamma_M
\simeq
\left\{
\begin{aligned}
& 0.38 \Gamma_0 & k_BT_b/m_ec^2\ll 1\\
& 0.34 \Gamma_0 & k_BT_b/m_ec^2\gg 1
\end{aligned}
\right.\,,
\end{equation}
for $\gammabeam\gtrsim10$, as seen in Figure \ref{fig:OGgen}.  Hence, unstable modes exists and robustly grow at roughly $\Gamma \approx 0.4\Gamma_0$ for nearly any value of $k_BT_b/m_ec^2$, wavevector orientation, and $\gammabeam \gg 1$.

@@

>>>>

Because there is little variation in the maximal oblique growth rate as a wavevector orientation, we plot the maximum growth rate as a function of $T_b$
and $\gammabeam - 1$ in Figure \ref{fig:OGgen}.  Here for relativistic beams, the maximum growth rate varies
little with $T_b$, varying by less than $10\%$ between hot and cold beams and 
we find:
\begin{equation}
\Gamma_M
\simeq
\left\{
\begin{aligned}
& 0.38 \Gamma_0 & k_BT_b/m_ec^2\ll 1\\
& 0.34 \Gamma_0 & k_BT_b/m_ec^2\gg 1
\end{aligned}
\right.\,,\label{eq:kinetic growth rate}
\end{equation}
for $\gammabeam\gtrsim10$, as seen in Figure \ref{fig:OGgen}.  Hence, unstable modes exists and robustly grow at roughly $\Gamma \approx 0.4\Gamma_0$ for nearly any value of $k_BT_b/m_ec^2$, wavevector orientation, and $\gammabeam \gg 1$.

@@

\phil{Finally, the growth rate that we derived here (Equation (\ref{eq:kinetic growth rate})) and that of BCP12 (their equation (16)) which is originally derived from the numerical fit of \citet{Bret-Grem-Beni:10} are exactly the same.  We must note, however, that the our definition of $T_b$ is in the COM frame whereas BCP12 defines $T_b$ in the ``lab'' frame.  As a result, there is a factor of $\gamma_b$ that is explicit in equation (\ref{eq:kinetic growth rate}) that is implicit in equation (16) of BCP12.   }
